---
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyr)
library(stringr)
library(DT)
library(highcharter)
library(plotly)
library(ggplot2)
library(RColorBrewer)
library(lubridate)


source("functions.R")

# knitr::opts_chunk$set(echo = TRUE)
working_dir <- ("/mnt/TB8Drive/Bidirect_Neuroimaging/BIDS/base_protocol/sourcedata/") 
setwd(working_dir)

metadata_df <- read_metadata()
metadata_df %>% count(level)
metadata_dataset <- metadata_df %>% filter(!is.na(Authors)) %>% extract_metadata(0)
metadata_level_0 <- metadata_df %>% filter(is.na(Authors)) %>% extract_metadata(0) # root folder data
metadata_level_1 <- metadata_df %>% filter(is.na(Authors)) %>% extract_metadata(1)
metadata_level_2 <- metadata_df %>% filter(is.na(Authors)) %>% extract_metadata(2)
metadata_level_3 <- metadata_df %>% filter(is.na(Authors)) %>% extract_metadata(3)
```

---
pagetitle: `r metadata_dataset$Name`
---

Overview
=======================================================================

Column {data-width=150}
-----------------------------------------------------------------------

### Dataset information

__Authors:__ `r metadata_dataset$Authors`  
__Funding:__ `r metadata_dataset$Funding`  
__How to acknowledge:__ `r metadata_dataset$HowToAcknowledge`  
__License__: `r metadata_dataset$License`  
__References and Links:__ `r metadata_dataset$ReferencesAndLinks`  
__BIDS Version:__ `r metadata_dataset$BIDSVersion`  
__Subject Regex:__ r metadata_dataset$subject_regex

### Total files

```{r}
valueBox(n_distinct(metadata_level_3$filename),
         icon = "fa-pencil")
```

### Unique Sessions

```{r}
valueBox(n_distinct(metadata_level_3$session),
         icon = "fa-pencil")
```

### Unique Subjects

```{r}
valueBox(n_distinct(metadata_level_3$subject),
         icon = "fa-pencil")
```

### Sequence Types

```{r}
valueBox(n_distinct(metadata_level_3$sequence),
         icon = "fa-pencil")
```




Column {data-width=500}
-----------------------------------------------------------------------

### Plot

```{r}
p <-metadata_level_3 %>%
  group_by(session, type, sequence) %>%
  count() %>%
  ggplot(aes(x = session, y = n, fill = sequence)) +
  geom_bar(stat="identity", position=position_dodge()) +
  theme_minimal() +
  facet_wrap(~type + sequence) +
  scale_fill_brewer(palette="Dark2")

ggplotly(p)
```


### Study information

```{r}
metadata_level_3 %>%
  group_by(session, type, sequence) %>%
  count() %>%
  spread(session, n) %>%
  DT::datatable(options = list(
  pageLength = 25
))
```


Metadata levels 
========================================================


Metadata {data-width=500}
-------------------------------------------------------------------------

### Metadata level 0 (root folder)

```{r}
metadata_level_0 %>%
  DT::datatable(options = list(
  pageLength = 25
))
```

### Metadata level 1 (subject folder)

```{r}
metadata_level_1 %>%
  DT::datatable(options = list(
  pageLength = 25
))
```


Metadata {data-width=500}
-----------------------------------------------------------------

### Metadata level 2 (session folder)

```{r}
metadata_level_2 %>%
  DT::datatable(options = list(
  pageLength = 25
))
```


Sensitive Information
===============================================================================
Extracted from JSON files

Column {data-width=150}
--------------------------------------------------------
### PatientID

```{r}
valueBox(sum(!is.na(metadata_level_3$PatientID)),
         icon = "fa-pencil")
```

### PatientName

```{r}
valueBox(sum(!is.na(metadata_level_3$PatientName)),
         icon = "fa-pencil")
```

### PatientBirthDate

```{r}
valueBox(sum(!is.na(metadata_level_3$PatientBirthDate)),
         icon = "fa-pencil")
```

### PatientSex

```{r}
valueBox(sum(!is.na(metadata_level_3$PatientSex)),
         icon = "fa-pencil")
```

### PatientWeight

```{r}
valueBox(sum(!is.na(metadata_level_3$PatientWeight)),
         icon = "fa-pencil")
```

### AcquisitionDateTime

```{r}
valueBox(sum(!is.na(metadata_level_3$AcquisitionDateTime)),
         icon = "fa-pencil")
```


Column {data-width=500}
--------------------------------------------------------

### Overview

```{r}



metadata_level_3 %>%
  select(
    subject,
    PatientID,
    PatientName,
    session,
    AcquisitionDateTime,
    PatientBirthDate,
    PatientSex,
    PatientWeight
  ) %>%
  mutate(AcquisitionDateTime = as.Date(AcquisitionDateTime)) %>%
  unique() %>%
  datatable_setting()

```

ID Validation
==================================================

Column {data.width = 500}
--------------------------------------------------------

### ID changes - Shapeshifters

```{r}

str_to_remove = regex("bi(b|d|dd)ire(c|k|tc)t|bd", ignore_case = TRUE)

clean_string <- function(input, pattern) {
  library(stringr)
  input %>%
    str_remove_all(pattern) %>%
    str_remove_all("[:punct:]+") %>%
    str_remove_all(str_to_remove)
  }

metadata_level_3 %>%
  select(session, subject, PatientID, PatientName) %>%
  mutate(
    subject = str_remove(subject, "sub-"),
    PatientID = clean_string(PatientID, subject),
    PatientName = clean_string(PatientName, subject)
  ) %>%
  filter(PatientID != "" | PatientName != "") %>%
  unique() %>%
  datatable_setting()
```

### Birthdata - Reincarnated

```{r}
metadata_level_3 %>%
  select(subject, PatientBirthDate) %>%
  unique() %>%
  count(subject) %>% filter(n > 1) %>%
  left_join(metadata_level_3) %>%
  select(subject, session, AcquisitionDateTime, PatientBirthDate) %>%
  mutate(AcquisitionDateTime = as.Date(AcquisitionDateTime)) %>%
  unique() %>%
  group_by(subject) %>%
  mutate(
    Age = difftime(AcquisitionDateTime, PatientBirthDate) %>% time_length("years") %>% round(1),
    BirthDateDiff = difftime(PatientBirthDate, lag(PatientBirthDate)) %>% time_length("years") %>% round(1)
  ) %>%
  datatable_setting()

```

Column {data.width = 500}
-----------------------------------------------------------

### Sex change - Clownfishes

```{r}
metadata_level_3 %>%
  select(subject, PatientSex) %>%
  unique() %>%
  count(subject) %>% filter(n > 1) %>%
  left_join(metadata_level_3) %>%
  select(subject, session, PatientSex) %>% unique() %>%
  datatable_setting()
      
    
  
```

### Two acquisition dates at same session - Time travellers

```{r}
metadata_level_3 %>%
  select(subject, session, AcquisitionDateTime) %>%
  mutate(AcquisitionDateTime = as.Date(AcquisitionDateTime)) %>%
  unique() %>%
  group_by(subject) %>%
  count(session) %>% filter(n > 1) %>%
  datatable_setting()
```

Sequence ID Validation
==========================================================================

```{r}
metadata_level_3 %>%
  select(type, sequence, SeriesDescription, ProtocolName) %>%
  group_by_all() %>%
  count() %>%
  datatable_setting()
```


Duplicates
==========================================================================

Column {data.width=500}
------------------------------------------------------------------------

### Identified duplicates
```{r}
metadata_level_3 %>%
  select(subject, session, sequence) %>% 
  group_by_all () %>% 
  count() %>% 
  filter(n > 1) %>%
  left_join(metadata_level_3) %>% 
  select(subject, session, sequence, filename) %>% 
  unique() %>%
  datatable_setting()
```

Settings - anat
================================================================================

### T1w

```{r}
show_settings("T1w") %>% datatable_setting()
```


### T2w

```{r}
show_settings("T2w") %>% datatable_setting()
```


### T2star

```{r}
show_settings("T2star") %>% datatable_setting()
```

### T1map

```{r}
show_settings("T1map") %>% datatable_setting()
```

### T2map
```{r}
show_settings("T2map") %>% datatable_setting()
```


### FLAIR
```{r}
show_settings("FLAIR") %>% datatable_setting()
```


### PD
```{r}
show_settings("PD") %>% datatable_setting()
```


### PDT2
```{r}
show_settings("PDT2") %>% datatable_setting()
```


### inplaneT1
```{r}
show_settings("inplaneT1") %>% datatable_setting()
```


### inplaneT2
```{r}
show_settings("inplaneT2") %>% datatable_setting()
```


### Angio
```{r}
show_settings("angio") %>% datatable_setting()
```


### Defacemask
```{r}
show_settings("defacemask") %>% datatable_setting()
```


### SWI
```{r}
show_settings("swi") %>% datatable_setting()
```


Settings - dwi
================================================================================

### DWI
```{r}
show_settings("dwi") %>% datatable_setting()
```


Settings - task
================================================================================

### Task

```{r}
show_settings("bold") %>% datatable_setting()
```

